\plaintitle

### 2016-08-25 drafts/labor/complexity.tex
moving complexity.tex stuff around

\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data,
telling coherent and compelling stories
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This diverse body of research has involved similar approaches to problems,
namely consisting of insights made by the Computer Science community.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{foundry,crowdForgeKittur}.

% \ali{the thing that has made all of this possible has been decomposition and the application of computational processes (e.g. MapReduce) to make it all possible}

@@

  \topic{A smaller but growing body of work has reflected on this
  and brought to our attention a number of ethical questions surrounding the
  increasing complexity of crowdwork and the hazards that increasingly arise.}
  \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
  --- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
  for instance ---
  but these and other dangers range an enormous landscape % too informal?
  \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.
% }

% \endnotetext{
  Nuke this?

@@

  Crowdforge, turkomatic, others talk about limiting factors; bring them up
}

\endnotetext{
    Talked to someone about this section and got some feedback\dots
    \begin{enumerate}
      \item Explain what ``clever arrangement of work'' in the first paragraph means
            (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
      \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
            (maybe even to justify its placement here); and
      \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
            to make the historical stuff on piecework
            directly speak to the three previous paragraphs.
      \item (Maybe?) summarize the piecework stuff
            (the last paragraph approaches that, but more could be done).
    \end{enumerate}
    Thoughts on this?
}

\topic{The research into piecework has identified a number of
major constraints that we should expect to find when
applying piecework approaches to labor markets.}
% To illustrate this, we look to 
% First, we look to
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
\citeauthor{Brown01041990} makes a more assertive
claim about the factors necessary for piecework to thrive,
specifically arguing that
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} makes another claim that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.

\ali{\citeauthor{10.2307/23702539} also argues that
a significant obstacle to the introduction of piecework in railroad shops was
the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely
if ever
interact face--to--face and
opportunities for coordination and collective action are severely limited,
we should expect to see
the challenges stymieing collective action
that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.}

\topic{}
% \topic{While much of the above work has focused on
% clever arrangements of systems to manage collectives of workers,
% another body of work has turned inward toward managing the self.}
\citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
(of sorts)
will prove relevant as we trace the literature surrounding piecework.

>>>>

\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems,
often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.

\topic{This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.}
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed,
just like non--expert teams
\cite{foundry}.

\topic{The research into piecework has identified a number of
major constraints that we should expect to find when
applying piecework approaches to work.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
\citeauthor{Brown01041990} makes a more assertive
claim about the factors necessary for piecework to thrive,
specifically arguing that
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} makes another claim that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.

\topic{\joke{great} topic sentence here.}
% \topic{While much of the above work has focused on
% clever arrangements of systems to manage collectives of workers,
% another body of work has turned inward toward managing the self.}
\citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
(of sorts)
will prove relevant as we trace the literature surrounding piecework.

@@

  \topic{A smaller but growing body of work has reflected on this
  and brought to our attention a number of ethical questions surrounding the
  increasing complexity of crowdwork and the hazards that increasingly arise.}
  \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
  --- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
  for instance ---
  but these and other dangers range an enormous landscape % too informal?
  \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

  kill this?

@@

  Crowdforge, turkomatic, others talk about limiting factors; bring them up

    Talked to someone about this section and got some feedback\dots
    \begin{enumerate}
      \item Explain what ``clever arrangement of work'' in the first paragraph means
            (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
      \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
            (maybe even to justify its placement here); and
      \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
            to make the historical stuff on piecework
            directly speak to the three previous paragraphs.
      \item (Maybe?) summarize the piecework stuff
            (the last paragraph approaches that, but more could be done).
    \end{enumerate}
    Thoughts on this?

\citeauthor{10.2307/23702539} also argues that
a significant obstacle to the introduction of piecework in railroad shops was
the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely
if ever
interact face--to--face and
opportunities for coordination and collective action are severely limited,
we should expect to see
the challenges stymieing collective action
that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.

}

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  \nobalance{}
  \begin{appendices}
  \theendnotes
  \end{appendices}
}

### 2016-08-25 drafts/labor/trackingWork.tex
friday edits, mostly rearranging, some additions
moving complexity.tex stuff around

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

% \bibliographystyle{SIGCHI-Reference-Format}

\makeatletter
\def\blx@maxline{77}
\makeatother

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[al2: #1]}}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences
\newcommand{\joke}[1]{#1} % if you're in a subfile, bold the \topic sentences

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

% \bibliographystyle{SIGCHI-Reference-Format}
\renewcommand*{\notesname}{Graveyard of old paragraphs}
\makeatletter
\def\blx@maxline{77}
\makeatother

@@

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\definecolor{BrickRed}{HTML}{FF0000}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{BrickRed}[al2: #1]}}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, bold the \topic sentences
